\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{DHUSHYANTH R} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91-6369676998 \\ Dharapuram, TamilNadu} 
\address{\href{mailto:dhushyanthravichandran@gmail.com}{dhushyanthravichandran@gmail.com} \\ 
\href{https://www.linkedin.com/in/dhushyanth-ravichandran-798a52242}{linkedin-dhushyanth-ravichandran} \\ 
\href{https://github.com/DhushyanthRavichandran}{github-dhushyanth-ravichandran}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{
As a third-year electronics engineering student, I'm driven by my passion for the field to constantly learn and grow. I'm eager to contribute to the organization's success and my own development, with a collaborative and team-oriented mindset.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering}, KONGU ENGINEERING
COLLEGE
 \hfill {Expected 2025}\\
Electronics and Communication Engineering \\
CGPA: 7.66

{\bf Schooling}, GNANASAMBANDAR MATRIC
HR SEC SCHOOL \\
HSC-Percentage: 89\% \hfill {2019-2020}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C, Java, Python,Javascript
\\
Technologies &  Machine Learning, Pandas, Numpy, HTML, CSS, SQL\\
Soft Skills & Adaptability, Team work, Focused\\

\end{tabular}\\
\end{rSection}

\begin{rSection}{Areas of Interest}
\begin{tabular}{@{}l}

Machine Learning \\
Web Development\\
Digital Electronics 
\end{tabular}
\end{rSection}

\begin{rSection}{Projects}

\textbf{KEC-Ideathon | Kongu Engineering College} \\
\textit{Autonomous Bot for Sensing Soil Moisture and Valve Regulation} \hfill {29.9.2023}\\
Developed an autonomous bot for sensing soil moisture and valve regulation, winning the 2nd Prize at KEC Ideathon. Awarded a cash prize of INR 1500 for the project.

\textbf{On Machine Learning} 

\textbf{\textit{NeuroPulse| Your Personal Stroke Prevention Companion}} \hfill {2.4.2024}
Developed NeuroPulse, a Flask-based website using a Random Forest algorithm to predict strokes, showcasing a passion for impactful healthcare technology and the integration of machine learning into web development. Explored advancements in stroke prediction, prevention, and community engagement.\\
GitHub Repository: \url{https://github.com/DhushyanthRavichandran/NeuroPulse} \\
Website: \url{https://neuropulse.onrender.com/}

\textbf{\textit{Wine Classification Model}} \hfill {27.12.2023}\\
Crafted a Wine Classification model distinguishing red and white wines, showcased on a Streamlit website and GitHub. Eager to apply insights for impactful solutions. Developed Wine Classification model utilizing XGBoost algorithm. \\
Github Repo: \href{https://github.com/DhushyanthRavichandran/Wine-Prediction}{\textbf{\url{https://github.com/DhushyanthRavichandran/Wine-Prediction}}} \\
Website: \href{https://wine-prediction.streamlit.app/}{\textbf{\url{https://wine-prediction.streamlit.app/}}}

\end{rSection}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Online courses}
\begin{tabular}{ll}
IBM \hspace{3em} Data Analysis with Python  \hspace{28em} 8.2.2024 \\
Kaggle \hspace{2em} Intro to Machine Learning \hfill 11.2.2023 \\
Oracle \hspace{2em} OCI AI Foundations Associate \hfill 17.2.2024 \\
IBM \hspace{3em} SQL and Relational Databases 101 \hfill 1.2.2024
\end{tabular}

\end{rSection}
\end{document}
